---
title: "Final-ABS"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
library(foreign)
library(tidyverse)
library(DMwR2)
library(e1071)
library(glmnet)
library(knitr)
merge <- read.spss("data/W1 Merged Data/Wave.1_Data/Merge/Wave1_20170906.sav",
                  to.data.frame=TRUE)
```

## Introduction: 

After looking through the questions, we decided that in the time given, we should focus on building a model that can predict q106, which asks if the respondent thinks equal treatment of citizens by their government has gotten better or worse. We believe this question is important in order to compare how different respondents have viewed trends towards a "better" government system in their country. For instance, it's possible that a perception of positive trends is strongly correlated with a specific country or demographic group, indicating targeted improvements in equality. Alternatively, if perceptions of unequal treatment are strong correlated with certain groups, these groups may have been disproportionately "left out" of recent progress. 

Overall, this analysis could provide grounds for further research into how different groups perceive recent developments around equality in East and Southeast Asia.


## EDA:

Before starting our exploratory data analysis, we subsetted the merged Wave 1 data to only include the most important variables as provided in the documentation. 

Afterwards, we explored which variables had the most missing data and investigated whether data was randomly or non-randomly missing (see Table 1 in the appendix). We discovered that there was no data for se004, q121, and q028 from Mainland China and no data on respondent age from Mongolia. 

After visualizing the breakdown of responses to our variable of interest by age group (table 2), we determined that age was unlikely to be a significant predictor in our final model. Due to the missing data, we decided to drop se004, q121, q028, and se003a from our dataset.

After visualizing our variable of interest (Graph 1), we determined that there were a good number of observations for each category of our response variable. This allowed us to proceed with putting together a multinomial lasso model. 

## Proposed Methodology:
Our selected variables:
se002(gender), se005(education), se009(income), country, q027(participation in last election), q105(everyone is free to say what they think)

In building our model, we used various methods to narrow down a range of potentially strong and important predictor variables. 

First off, we choose to include a few typical indicators of socio-economic status as predictor variables -- gender, education level, and income level. These _______.
Although we considered adding age as a predictor, we found that there was significant missing data on age from Mongolia, and it was therefore compromised as a predictor variable. Our exploratory data analysis confirmed that age was likely not a significant predictor of responses to our question of interest, so we proceeded without age (see appendix).

In addition, we added question q105 as a predictor, which asked whether survey respondents felt that free speech was getting better or worse in their country. We felt that this was potentially relevant to include, because perspectives on equality and free speech are tied to a survey respondent’s notions of rights and justice. There were no systematically missing observations from q105 and no obvious barriers to it being a predictor variable. 

Finally, we included country because country is a key aspect of the response variable we are assessing. We are attempting to predict a survey respondent’s perspective on trends in their government’s equal treatment of citizens, so the respondent’s country is a key aspect to include. 


We decided to transform our response variable q106 into two different categories. "Much worse," "Somewhat worse," "Much the same," were encoded as 0, and "Somewhat better, "Much better than before" were encoded as 1. As a result, our goal is to predict if trends in the equal treatment of citizens has gotten worse/stayed the same, or gotten better. We decided to drop all NA's from the dataframe. We considered using KNN to impute missing values, but we thought the missing data may have a systematic pattern, as seen in the Table 1, and the large amount of missing values were computationally expensive to fit given the number of dimensions. 

We then decided to fit a logistic lasso regression in order to decrease the variance of our model and also perform variable selection. Shrinkage of the coefficients also may help with multicollinearity in the model. We used cross validation to find the optimal lambda shrinkage parameter, and used that as the lambda parameter in our final model. 

## Analysis: 

```{r, include=TRUE}
data_merge1 <- merge%>%
   select(se002, se005, se009, country, q027, q105, q106)

data_merge1 <- data_merge1%>% 
  drop_na() 


data_merge1 <- data_merge1%>% 
   mutate(q106 = case_when(q106=="Much worse" ~ 0,
                           q106=="Somewhat worse" ~ 0,
                           q106=="Much the same" ~ 0,
                           q106=="Somewhat better" ~ 1,
                           q106=="Much better than before" ~ 1,))
x <- model.matrix(q106~.,data_merge1)[,-1]

y <- data_merge1$q106
#Finding optimal lambda shrinkage value to reduce error through cross validation
set.seed(123)
cv.lasso <- cv.glmnet(x, y, alpha = 1, family = "binomial")
#Creation of lasso model and outputting regression coefficients
lasso_model <- glmnet(x, y, alpha = 1, family = "binomial",
lambda = cv.lasso$lambda.min)
coef(lasso_model)
cv.lasso$lambda.min
```

Looking at our model, we see that certain levels of some predictors may have coefficients of 0, but for all predictors most if not all levels are nonzero and significant. We can tell that for example, a female is less likely to think that equal treatment of people by the government has gotten better. Countries Mainland China, Mongolia, and Thailand seem to have be more likely to think that equal treatment of people by the government has gotten better. Meanwhile, countries Hong Kong, Korea, Philippines, and Taiwan are less likely to think so. Interestingly enough, we found that compared to the 1st quintile of wealth (poorest), each other quintile of wealth is less likely to believe that equal treatment of people has gotten better. 

## Conclusion: 

Given more time, we would like to explore more interaction effects. In addition, we would also include Wave2 as a predictor variable and merge in the Wave2 data. Also, another thing we want to consider is the handling of missing data. Part of the reason we didn't use certain predictors, for example age, is because certain countries did not report them at all. We were wondering if there was a better way to fix this problem. Plenty of other observations had missing values as well, so we wanted to find a statistically sound way to impute them. Finally, we wanted to find other models that might fit well. For example, we fit a SVM but scrapped it because we were not sure about performing proper variable selection with SVM's. In addition, we would have liked to implement decision trees since they can handle categorical predictors and responses really well. 

## Appendix
```{r, include=FALSE}
merge <- merge %>% select(se002, se004, se005, se009, se003a, country, q007, q008, q009, q010, q006, q098, q128, q005, q027, q028, q105, q106, q121, q123, q127)
#glimpse(merge)
```
### Table 1 - table of missing values
```{r}
n <- length(merge %>% colnames())
missing_vec <- numeric(n)
for (i in 1:n) {
  nrow <- merge %>% select(colnames(merge)[i]) %>% filter(is.na((merge)[i])) %>% nrow()
  missing_vec[i] <- nrow
}
missing_vec
#merge %>% select(colnames(merge)[2]) %>% filter(is.na((merge)[2])) %>% nrow()
```
```{r}
#data frame
NA_table <- data.frame(colnames(merge), missing_vec)
kable(NA_table, col.names = c("Variable", "Number of NA"), caption = "Table of NA values")
```
### Table 2- Table of country breakdown
```{r}
country_percs <- merge %>% count(country) %>% mutate(perc = round(n / sum(n) * 100, digits = 3))
country_percs <- country_percs %>% arrange(perc) %>% select(-n)
kable(country_percs, col.names = c("Country", "Percent of Respondents"), caption = "Survey Respondents: Breakdown by Country" )
```
### Graph 1- Visualize Q106
```{r }
#Visualize key response var
ggplot(data = merge, mapping = aes(x = q106, fill = q106)) +
  geom_bar() +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + labs(title = "Is everyone treated equally by the government?") +
  xlab("Responses") +
  ylab("Number of Responses") +
  labs(fill="")
```

### Graph 2- Visualize Q106 by country

```{r}
#Visualize key response var by country
ggplot(data = merge, mapping = aes(x = q106, fill = q106)) +
  geom_bar() +
  facet_wrap("country") +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + labs(title = "Q106: Response by Country") +
  labs(fill = "") +
  ylab("Number of responses") +
  xlab("")
```

### Graph 3- Visualize Q106 by Gender

```{r}
merge_subg <- merge %>% drop_na(se002) %>%
  arrange(se002)
ggplot(data = merge_subg, mapping = aes(x = q106, fill = q106)) +
  geom_bar() +
  facet_wrap("se002") +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + labs(title = "Q106: Response by Gender") +
  labs(fill = "") +
  ylab("") +
  xlab("")
```

### Graph 4- Vizualize Q106 by Income

```{r}
merge_subi <- merge %>% drop_na(se009) %>%
  arrange(se009)
ggplot(data = merge_subi, mapping = aes(x = q106, fill = q106)) +
  geom_bar() +
  facet_wrap("se009") +
  theme(axis.text.x=element_blank(),
      axis.ticks.x=element_blank()) + labs(title = "Q106: Response by Income Level") +
  labs(fill = "") +
  ylab("Number of responses") +
  xlab("")
```

### Graph 5- age vs answer to Q106

```{r}
merge_sub <- merge %>% drop_na(se003a) %>%
  mutate(se003a = as.numeric(se003a)) %>%
  mutate(age_range = case_when(se003a <= 18 ~ "Under 18",
                               se003a > 18 & se003a <= 25 ~ "18-25",
                               se003a > 25 & se003a <= 50  ~ "25-50",
                               se003a > 50 & se003a <= 75  ~ "50-75",
                               se003a > 75 ~ "above 75")) %>%
  arrange(age_range)
merge_sub <- merge_sub %>% 
  mutate(age_range = factor(age_range, levels = c("Under 18", "18-25", "25-50","50-75", .))) %>%
  arrange(age_range)
ggplot(data = merge_sub, mapping = aes(x = q106, fill = age_range)) +
  geom_bar(position = "fill") +
  theme(axis.ticks.x=element_blank(),
        axis.text.x = element_text(angle = 25)) +
  labs(title = "Is everyone treated equally by the government?", x= "Response", y= "Count")
```

### Table 3- Response of Q106 by Country

```{r, message= FALSE}
table <- merge %>% group_by(country) %>% count(q106) %>% summarize(percent = round(n/sum(n)*100, digits =3), 'Q106 Response' = q106)
# table
# table %>% colnames()
newtble <- pivot_wider(table, names_from = country, values_from = percent)
kable(newtble, caption = "Country Breakdown of Response to Q106")
```
